Classless Java

### 2015-10-06 paper/sections/Formalization.tex
revised formalization

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{mmodifier}(m,C) = \textbf{static} }
{\Gamma \vdash C.m(\overline{e}) \in E}
\quad \textsc{(T-StaticInvk)}
\]
\marco{rule tInvk must check is not static?}
\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\\\
\textbf{this}:I \\  I <: C }
{\Gamma \vdash C.\textbf{super}.m(\overline{e}) \in E}
\quad \textsc{(T-SuperInvk)}
\]

\[
\inferrule[(Obj)]{
\forall i\in 1\ldots n\ \Gamma,\Gamma^{\mh_i}\vdash\e_i\in \_\subtype\C^{\mh_i}\\
\forall\mh\in \mhs \mbox{ such that }
\mBody(\m^\mh,\C)=\method;\mh\subtype\mh^\method\\
\forall\m \mbox{ such that }
\mBody(\m,\C)\in\{\mh\QM;,\conflicted\mh\QM;\} \exists \mh_i \in\mhs\mbox{ such that }\mh_i\subtype\mh\\
\Gamma=\Gamma',\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C\\
\mhs=\mh_1\ldots\mh_n
}{
\Gamma' \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\]

\subsubsection{Typechecking of Methods}

\marco{I can not understand those rules, when is t-meth and t-meth body called? when is that you state that all methods in all interfaces must be ok?}
\begin{comment}
\[
\inferrule
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

@@

\[
\inferrule
{\textbf{this}:I, \overline{x}:\overline{T} \vdash e:S \\ S <: T_0 \\
IT(I)=\text{interface } I \text{ extends } \overline{J} \text{\{...\}} \\
\forall i,\text{if \textsf{mtype}}(m,J_i) = \overline(T) \to U_0, \text{then }
T_0 <: U_0 }
{T_0 \spc m(\overline{T} \spc \overline{x}) \text{ \{ return } e;\} \text{ OK IN
    I} }
\quad \textsc{(T-MethBodyExt)}
\]

\subsubsection{Typechecking of Interfaces}
\[ \inferrule
{\textbf{interface } I \textbf{ extends } \overline{J} \{ \overline{M} \} \\\\
 \forall J_i \in \overline{J}, J_i \text{ OK} \\\\
 \forall m \in \overline{M}, \textsf{mbody}(m,I) \neq ERROR \\\\
 \forall J_i \in \overline{J}, \forall m \text{ inside } J_i,
 \textsf{mbody}(m,I) \neq ERROR }
{I \text{ OK}}
\quad \textsc{(T-Intf)}
 \]

@@

\override(\none,\method)=\method &\mif\ \method\neq \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\override(\method,\mh\QM;) & \method'\in\{\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \}\\
\override(\method,\mh')
=\method &\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}\\
& \mh\subtype\mh'\\
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}
\end{equation*}

@@

>>>>

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{mmodifier}(m,C) = \textbf{static} }
{\Gamma \vdash C.m(\overline{e}) \in E}
\quad \textsc{(T-StaticInvk)}
\]
%\marco{rule tInvk must check is not static?}
\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\\\
\textbf{this}:I \\  I <: C }
{\Gamma \vdash C.\textbf{super}.m(\overline{e}) \in E}
\quad \textsc{(T-SuperInvk)}
\]

\[
\inferrule{
\forall i\in 1\ldots n\ \Gamma,\Gamma^{\mh_i}\vdash\e_i\in \_\subtype\C^{\mh_i}\\
\forall\mh\in \mhs \mbox{ such that }
\mBody(\m^\mh,\C)=\method;\mh\subtype\mh^\method\\
\forall\m \mbox{ such that }
\mBody(\m,\C)\in\{\mh\QM;,\conflicted\mh\QM;\} \exists \mh_i \in\mhs\mbox{ such that }\mh_i\subtype\mh\\
\Gamma=\Gamma',\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C\\
\mhs=\mh_1\ldots\mh_n
}{
\Gamma' \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\quad \textsc{(T-Obj)}
\]

\subsubsection{Method Typing}

\begin{comment}
\[
\inferrule
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

@@

\[
\inferrule
{\textbf{this}:I, \overline{x}:\overline{T} \vdash e:S \\ S <: T_0 \\\\
IT(I)=\text{interface } I \text{ extends } \overline{J} \text{\{...\}} \\\\
\forall i,\text{if \textsf{mtype}}(m,J_i) = \overline(T) \to U_0, \text{then }
T_0 <: U_0 }
{T_0 \spc m(\overline{T} \spc \overline{x}) \text{ \{ return } e;\} \text{ OK IN
    I} }
\quad \textsc{(T-MethBodyExt)}
\]

\subsubsection{Interface Typing}
\[ \inferrule
{\textbf{interface } I \textbf{ extends } \overline{J} \{ \overline{M} \} \\\\
 \forall J_i \in \overline{J}, J_i \text{ OK} \\\\
 \forall m \in \overline{M}, \textsf{mbody}(m,I) \neq \error \\\\
 \forall J_i \in \overline{J}, \forall m \text{ inside } J_i,
 \textsf{mbody}(m,I) \neq \error }
{I \text{ OK}}
\quad \textsc{(T-Intf)}
 \]

@@

\override(\none,\method)=\method &\mif\ \method\neq \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\override(\method,\mh\QM;) & \method'\in\{\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \}\\
\override(\method,\mh')
=\method &\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}\\
& \mh\subtype\mh'\\
\override(\_,\_)=\error & Otherwise
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}
\end{equation*}

@@

\subsubsection{Auxiliary function:???}

\begin{equation*}
\begin{array}{ll}
\textsf{ofMethod}(C_0) = ... & ... \\
\textsf{otherMethod}(C_0) = \methods_1; \methods_2 \hspace{0.1in} & \mif\ \textsf{resolve}(C_0) = \overline{field} \\
& \method_1 = \textsf{with}(field, C_0) \\
& \method_2 = \textsf{clone}(field, C_0) \\
\textsf{resolve}(C_0) = \overline{field} & \mif\ \textsf{methods}(C_0) = \mhs \\
& \forall \mh \in \mhs, \mh \textsf{ isField or isWith or isClone or isDefault} \\
& \forall field \in \overline{field},\ \mh^{field} = T\ m\oR\cR,\ \mif\ \mBody(m, C_0) = T\ m\oR\cR\QM; \\
\textsf{methods}(C_0) = \mhs\ \bigcup\ \overline{\textsf{methods}(C)} & \mif\ \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \} \\
& \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \} \\
\textsf{with}(field, C_0) = T_0\ \QM{with}m\oR T\ x\cR\QM; & \mif\ \mh^{field} = T\ m\oR\cR,\ \mh' = T'\ \QM{with}m\oR T\ x\cR \\
& \mBody(\QM{with}m, C_0) \in \{ \mh'\QM;, \QM{default}\ \mh' \mbox{\Q@\{return \_;\}@}\} \\
& IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \},\ T_0 <: T' \\
\textsf{clone}(field, C_0) = T_0\ \QM{clone}\oR\cR\QM; & \mif\ IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \}
\end{array}
\end{equation*}

\haoyuan{``\textsf{isField or isWith or isClone or isDefault}''?}
